---
title: "Cleaning"
author: "Francesca Giacco"
date: "2023-02-22"
output: html_document
---

```{r}
#load packages 
library(tidyverse)
library(tidyr)
library(forcats)
library(stm)
library(quanteda)
library(quanteda.textstats)
library(stringr)
```

```{r}
#load data 

#scraped articles
d20<- read_csv("df2021.csv")
head(d20)


#get one line for every article
v<- paste("l_", letters, sep="")

d1<- d20 %>% separate(links, v,  "'https?://" )%>% 
  mutate(victim=tolower(victim))


d2<-d1 %>%
  select(-c(l_a)) %>% 
  pivot_longer(
    cols = starts_with("l_"),
    names_to = "article",
    names_prefix = "wk",
    values_to = "link",
    values_drop_na = TRUE
  ) 

d3<- d2 %>%  separate(link, c("link", "title", "newspaper"),  "('|\"), " ) 

head(d3)

#save dataset
write.csv(d3, "d3.csv", row.names=FALSE)


#dataset with info about femicide - "Non una di meno"
info21<- read_csv("data2021.csv")

clean_info<- info21 %>%  
             mutate(victim=tolower(paste0(Nome," ", Cognome)))



#merge datasets (cleaned manually)

data21<- read.csv("data2021-new2.csv", sep=';' , header=TRUE) %>% 
    mutate(victim=tolower(paste0(Nome," ", Cognome)))

d4<- read.csv("d4.csv", sep=';' , header=T)
  

#merge the two datasets  by victim name 
merged2<- merge(data21, d4, by="victim", all.x=T) %>% 
        rename("date"="Data.morte") %>% 
        mutate(date= as.Date(date, format = "%d-%b-%Y"))  %>% 
        arrange(date) %>%  
        mutate(newspaper=gsub('[[:punct:] ]+', ' ',newspaper))
          

merged3<- merged2 %>% 
        mutate(link= ifelse(is.na(link), Link.fonte.media, link))

#save dataset - this dataset contains all the links, not the article texts 
#

write.csv(merged3, "merged.csv", row.names=FALSE)


```
I have added the texts to all the links (manually). In a later stage or for reproduction purpose, better to use the package "Newsplease" on Python. 
The new file is called "merged-merged.csv"

```{r}
datac<- read.csv("merged-merged.csv")

colnames(datac)

datac<- datac %>% 
  mutate(text=str_replace_all(text, "[\r\n]" , " ")) %>% 
  subset((!is.na(text))) %>% 
  mutate(tit=str_replace_all(title, "[\r\n]" , " ")) 
  
datac <- with(datac, datac[!(text == "" | is.na(text)), ])
datac <- with(datac, datac[!(tit == "" | is.na(tit)), ]) 

write.csv(datac, "datac.csv", row.names=FALSE)



```


After having added the victim blaming scores, I need to clean the column and keep only the score. 

```{r}
#dws<-read_csv("datawscores2.csv")

colnames(dws)

#dws<- dws %>% 
 mutate(tit_vb= as.numeric(str_extract(tit_vb, "[0-9].[0-9]+"))) %>% 
   mutate(text_vb= as.numeric(str_extract(text_vb, "[0-9].[0-9]+")))
 
 
dws<-read_csv("datawscores3.csv")

dws<- dws %>% 
 mutate(text_vb= as.numeric(str_extract(text_vb, "[0-9].[0-9]+"))) %>% 
   mutate(text_ab= as.numeric(str_extract(text_ab, "[0-9].[0-9]+"))) %>% 
      mutate(text_ob= as.numeric(str_extract(text_ob, "[0-9].[0-9]+"))) %>% 
      mutate(text_cb= as.numeric(str_extract(text_cb, "[0-9].[0-9]+"))) %>% 
      mutate(text_nb= as.numeric(str_extract(text_nb, "[0-9].[0-9]+")))

dws<- dws %>%
  mutate(gender.j=as.character(gender.j)) %>% 
  mutate(journalist=as.character(journalist)) %>% 
    mutate_at(c("gender.j", "journalist"), ~replace_na(.,"unknown"))

#check that it is numeric
class(dws$ass_blame)
#save dataset with clean scores

```

# Divide info about pictures content
```{r}

table(dws$content)

dws<- dws %>% 
  #mutate(vict_blamer=round(vict_blame, 2)) %>% 
  #only differenciate btw italian/non italian
  mutate(killer_origin=factor(ifelse(Paese.di.origine.presunt..colpevole=="Italia", "ita", "noita"))) %>% 
  mutate(victim_origin=factor(ifelse(Paese.di.origine.persona.uccisa=="Italia", "ita", "noita"))) %>% 
  #make age categorical
  mutate(agev=ifelse(Età.persona.uccisa<5, "baby", 
             ifelse(Età.persona.uccisa<15, "kid", 
             ifelse(Età.persona.uccisa<25, "adolescent", 
             ifelse(Età.persona.uccisa<40,"early_adult", 
             ifelse(Età.persona.uccisa<60,"adult", 
             ifelse(Età.persona.uccisa<70 ,"early_old", "old" ))))))) %>% 
  mutate(agec= ifelse(Età.presunt..colpevole<25, "adolescent", 
             ifelse(Età.presunt..colpevole<40,"early_adult", 
             ifelse(Età.presunt..colpevole<60,"adult", 
             ifelse(Età.presunt..colpevole<70 ,"early_old", "old" )))))%>% 
  mutate(gender.j=ifelse(gender.j==0, "man",
                  ifelse(gender.j==1, "woman", 
                  ifelse(gender.j==2, "both",
                  ifelse(gender.j==3, "woman",
                  ifelse(gender.j==4, "man", "unknown" )))))) 


  #attention: everytime it multiplies by 100
  dws<- dws %>% mutate(text_vb=text_vb*100) %>% 
  #mutate(tit_vb=tit_vb*100) %>% 
  
  mutate(relazione= ifelse(Relazione.con.la.persona.uccisa..semplificata.=="marito"|Relazione.con.la.persona.uccisa..semplificata.=="partner", "marito/partner", 
                    ifelse(Relazione.con.la.persona.uccisa..semplificata.=="altro", "altro", 
                    ifelse(Relazione.con.la.persona.uccisa..semplificata.=="conoscente", "conoscente", 
                    ifelse(Relazione.con.la.persona.uccisa..semplificata.=="ex partner", "ex partner", "altro/a parente"))))) %>% 
   mutate(content=str_replace(content, "victim, killer", "v&a")) %>% 
   mutate(content=str_replace(content, "killer, victim", "v&a")) %>% 
  mutate(cvict=ifelse((str_detect(content, "victim")), 1, 0)) %>% 
  mutate(cvanda=ifelse((str_detect(content, "v&a")), 1, 0)) %>% 
  mutate(cass=ifelse((str_detect(content, "killer")), 1, 0)) %>% 
  mutate(ccarpol=ifelse((str_detect(content, "carabinieri")), 1, 
                ifelse((str_detect(content, "police")), 1,0))) %>% 
   mutate(camb=ifelse((str_detect(content, "ambulance")), 1, 0)) 
 

head(dws)



write.csv(dws, "dws_clean.csv", row.names=FALSE)

```


# prepare data to use the model at sentence level. 
```{r}

head(dws)
n<-c(1:100)

v<- paste("n_", n, sep="")

sent_datac<- dws %>% 
  mutate(text2=text) %>% 
           separate(text2, v,  "\\." )
 

sent_datac<-sent_datac %>%
  pivot_longer(
    cols = starts_with("n_"),
    names_to = "code",
    names_prefix = "wk",
    values_to = "sentence",
    values_drop_na = TRUE
  ) 

sent_datac <- with(sent_datac, sent_datac[!(sentence == "" | is.na(sentence)), ])

sent_datac<- sent_datac %>% 
             mutate(n_char= nchar(sentence)) %>% 
             subset( n_char>34)
            

nchar(sent_datac$sentence[7])
                   
#save dataset
write.csv(sent_datac, "datawsent.csv", row.names=FALSE)


head(sent_datac)
```

Now that I have a score for every sentence, mean over each article. 

```{r}
dws2<-read_csv("datawscores3.csv")

colnames(dws)

dws<- dws %>% 
 mutate(sentence_vb= as.numeric(str_extract(sentence_vb, "[0-9].[0-9]+"))) 
   

ggplot(dws, aes(x=sentence_vb)) + geom_histogram()

#save dataset with clean scores
#write.csv(dws, "dws_clean3.csv", row.names=FALSE)

dws2<- dws %>% 
  group_by(title) %>% 
  summarise(mean(sentence_vb)) %>% 
  mutate(ms=dws2$`mean(sentence_vb)`)

         
ggplot(dws2, aes(x=ms)) + geom_histogram()

       
       
```


# With data obtained from Newsplease
```{r}
np<- read_csv("newsplease.csv") %>% 
  select(c("title", "text_new" ))

#merge the two datasets  by victim name 
merged_new<- merge( dws,np,  by="title", all.x=T) %>% 
  rename("article_n"="...1")
       
          
```


```{r}

n<-c(1:30)

v<- paste("n_", n, sep="")

para<- merged_new %>% 
separate(text_new, v,  "\n" )


para<-para%>%
  pivot_longer(
    cols = starts_with("n_"),
    names_to = "code",
    names_prefix = "wk",
    values_to = "paragraph",
    values_drop_na = TRUE
  ) 

para<- para %>%  
  mutate(len_par=nchar(paragraph))

ggplot(para, aes(x=len_par))+ geom_histogram()

table(para$code)


para2<- para %>%  
  subset(nchar(paragraph)>50)

para <- with(para, paragraph[!(paragraph == "" | is.na(parapr)), ])


write.csv(para, "paragraphs.csv", row.names=FALSE)
```




